---
title: "Article 2:	Information-Seeking Behavior Decision-Making between Online Search and Interpersonal Networks: The Case of Covid-19 Vaccinations "
author: "Kelsey Gonzalez"
date: "`r format(Sys.time(), '%d %B, %Y')`"
editor_options:
  chunk_output_type: console
output:
  bookdown::pdf_document2: 
    latex_engine: xelatex
    number_sections: true
  bookdown::word_document2: 
    toc: true
    reference_docx: StylesTemplate.docx
header-includes:
   - \usepackage{siunitx}
   - \usepackage{setspace}
   - \usepackage{dcolumn}
   - \usepackage{caption}
   - \usepackage{longtable}
   - \usepackage{booktabs}
   - \doublespacing
   - \usepackage{placeins}
csl: american-sociological-association.csl
bibliography: "My Library.bib"
indent: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE,
                      warning = FALSE,
                      cache = TRUE,
                      fig.width = 7,
                      fig.asp = 0.8,
                      out.width = "80%",
                      fig.align="center"
                      # dev.args = list(png = list(type = "cairo"))
                      )



if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, glue, extrafont, here, jtools, rms, modelsummary, showtext,thematic, kableExtra)


rain <- read_rds(here('data', 'RAiN_vacc_clean.rds')) %>% 
  mutate(across(where(is.logical), as.factor),
         date = lubridate::as_date(EndDate)) 

my_palette = c('#56b4e9','#999999','#E69F00','#009E73','#CC79A7','#0072B2','#D55E00','#E69F00')
my_palette  <- c(MetBrewer::met.brewer(name = 'Cross', type = 'discrete'), '#555F61')

## Automatically use showtext to render text
font_add_google("Open Sans", "open_sans")
showtext_auto()

theme_diss <- function(base_size = 14) {
  theme_minimal(base_size = base_size) %+replace%
    theme(
      # Figure assembly
      plot.title = element_text(family="open_sans",
                                size = rel(1), 
                                face = "bold",
                                margin = margin(0,0,5,0), 
                                hjust = 0),
      plot.title.position = "plot",
      plot.subtitle = element_text(family="open_sans",
                                   size = rel(0.85)),
      plot.caption = element_text(family="open_sans",
                                  size = rel(0.70),
                                  hjust = 1),
      # Graphical Zones
      panel.grid.minor = element_blank(),
      panel.border = element_blank(),
      # Axes
      axis.title = element_text(family="open_sans", 
                                size = rel(0.85),
                                face = "bold"),
      axis.text = element_text(family="open_sans", 
                               size = rel(0.70), 
                               face = "bold"),
      axis.line = element_line(color = "black", 
                               arrow = arrow(length = unit(0.3, "lines"), 
                                             type = "closed")),
      # Legend
      legend.title = element_text(family="open_sans",
                                  size = rel(0.85), 
                                  face = "bold"),
      legend.text = element_text(family="open_sans", 
                                 size = rel(0.70), 
                                 face = "bold"),
      legend.key = element_rect(fill = "transparent", 
                                colour = NA),
      legend.key.size = unit(1.5, "lines"),
      legend.background = element_rect(fill = "transparent", 
                                       colour = NA),
      # Facetting 
      strip.background = element_rect(fill = "#17252D",
                                      color = "#17252D"),
      strip.text = element_text(family="open_sans",
                                size = rel(0.85), 
                                face = "bold", 
                                color = "white", 
                                margin = margin(5,0,5,0))
    )
}

theme_set(theme_diss()) 

```

# Intro
It is unclear how individuals choose to search for information through the
multimedia environment of the 21st century. Much of the research conducted in
social networks and communication focus on senders, influencers, and persuasion
strategies (Merton 1968) rather than on “the receiver as an active information
seeker and processor. " (Johnson and Meischke 1993).

Core discussion networks are the default lens to investigate network resources
and social support in surveys. The underlying assumption is that individuals
reach out to a handful of strong ties when in need of support, which can be
elicited in surveys using name generators (Marsden 1987). This approach has
yielded important insights, but largely overlooks crucial processes of resource
activation (Hurlbert, Haines, and Beggs 2000; Perry and Pescosolido 2015; Smith
2005). Small (2017) shows that the core discussion network does not capture how
people activate social support in practice and indicates that people draw on
much broader social connections for support, also calling back to the weak ties
research by Granovetter (1973). There is ongoing research investigating how
weak-tie support holds for different support types based on the architecture put
forward by House, Umberson, and Landis (1988) of instrumental, emotional, and
informational support (Legewie and Gonzalez 2020). I follow the definition of
Cohen and Wills (1985) and define informational support as “help in defining,
understanding,  and coping with problematic events and include education,
advice, or referral to another source of  support” (Winemiller et al. 1993:640).

However, informational support can also be sought outside of the social network
context, namely via computer-mediated information search tools such as the
process of “Googling”. As the online environment began penetrating all facets of
modern human life, it makes sense that performing online search has become one
*f the most convenient vehicles for information search. While Small (2017)
focuses on how support can depend on a network tie simply "happened to be
there", online search is theoretically the most frictionless and costless mode
*f support. There are three computer-mediated vehicles I consider for this
analysis: search engines like Google, posting questions on online forums like
subreddits or Facebook groups, and posting a status update online via Facebook
*r Twitter. The first two comprise what I call “online search”, while the third
is conceptually distinct and important to include in the survey; yet, it is a
hybrid of social network activation and online search.

As online search or interaction also allows increased anonymity, no or lowered
social cost, and the potential avoidance of embarrassment and other negative
social interactions, I theorize that a majority of people who searched for
information will have done so online.

For this paper, I will use the case of Covid-19 vaccinations to explore the
variation among information search vehicles. There are theoretical reasons why
individuals would choose to search for information among their network ties
instead of online search. For instance, Rains (2018) finds that patients tend to
search for technical information about an illness online but turn to their
social network for experiential information from others facing similar
circumstances in the case of cancer. Moreover, if an individual distrusts the
medical establishment, or popular media, they may be more likely to activate
informational support among their social network or turn to online groups that
validate their worldview (Bogers and Wernersen 2014).

This research project is important because the vehicles used to search by people
impacts the information they are exposed to. Given the large swaths of both
misinformation and disinformation regarding Covid-19 (Motta, Stecula, and
Farhart 2020; Pathak, Agarawalla, and Gupta 2020; Shahsavari et al. 2020) and
the measurable impacts this misinformation has had on pandemic-related health
behaviors, how we choose to search for information affects our own lives and the
lives of others. Moreover, individuals who do not utilize social networks for
information search may feel like they have no network support, leading to
feelings of network isolation with major implications for mental health (Thoits
2011).

## section B: Research Questions
* How do computer-mediated or interpersonal network information-seeking strategies vary across populations? 
* What factors lead people to perform health information search online versus among social network ties? 
* How does the utilization of social networks, search engines, and social media as vary in the case of searching for information on the Covid-19 vaccine? 


# Research Methodology
The data used for this research project are based on original survey data sampled between `r format( min(rain$date), '%B %d, %Y')`  through `r format(max(rain$date), '%B %d, %Y')`.
- grant sample
- MTurk
- Dates 
- Locations

## Descriptive Statistics

###  Dependent Variables 
search for info
int_sought_


search for info by type
int_sought_fr_pers  
int_sought_fr_dr    
int_sought_fr_onlgroup
int_sought_fr_onlnet
int_sought_fr_onlsearch


vaccination view
vacc_view_pos

### Independent Variables
 receive_i_fr_dr   
receive_i_fr_pers      
receive_i_fr_tv    
receive_i_fr_onlnet    
receive_i_fr_onlgroup 

age 
gender 
race_white   
race_black    
race_nat      
race_asian 
hispanic
college





I received a $7,193 grant from the Summer Institute of Computational Social
Science to conduct research on network activation. Because I am co-PI on this
grant with my colleague Nicolas Legewie (University of Pennsylvania,
Humboldt-University of Berlin), I established permissions early-on in our
planning process to introduce and ‘own’ a few specific survey questions for
independent research on network versus non-network information activation.

The majority of this survey is a replication of the survey conducted in Mario
Small’s Book, Someone to Talk To (2017). We aim to expand on Small’s finding
that people draw on much broader sources than “important people” for support by
investigating how this theory of weak-tie support holds for different support
types (instrumental, emotional, and informational support; (see House et al.
1988)).

We aim to conduct surveys with 900 participants. The sample population for our
main survey are adult, non-institutionalized US residents. To adjust for the
non-representative sample provided by Amazon Mechanical Turk where we will host
the survey, we will use post-stratification weights based on the demographic
profile of each respondent (Wang et al. 2015).


```{r desc-table-1}
#| results = "asis"

desc_table <- rain %>% 
  select(receive_i_fr_dr,
  receive_i_fr_pers,
  receive_i_fr_tv,
  receive_i_fr_onlnet,
  receive_i_fr_onlgroup,
  int_sought,
  int_sought_fr_pers,
  int_sought_fr_dr,
  int_sought_fr_onlgroup,
  int_sought_fr_onlnet,
  int_sought_fr_onlsearch,
  int_sought_affect,
  vacc_status,
  vacc_view_pos,
  race_white,
  race_black,
  race_nat,
  race_asian, 
  hispanic,
  college,
  age, receive_i) %>% 
  as.data.frame()

datasummary(formula = 
  (`Received info` = receive_i) +
    (`Received info, Doctor` = receive_i_fr_dr) +
    (`Received info, Person` = receive_i_fr_pers) +
    (`Received info, News` = receive_i_fr_tv) +
    (`Received info, Social Networking Site` = receive_i_fr_onlnet) +
    (`Received info, Online Forum` = receive_i_fr_onlgroup) +
    (`Sought Info` = int_sought) +
    (`Sought Info, Doctor` = int_sought_fr_dr) +
    (`Sought Info, Person` = int_sought_fr_pers) +
    (`Sought Info, Social Networking Site` = int_sought_fr_onlnet) +
    (`Sought Info, Online Forum` = int_sought_fr_onlgroup) +
    (`Sought Info, Online Search` = int_sought_fr_onlsearch) +
    (`Vaccination Status` = vacc_status) +
    (`Vaccination Favorability` = vacc_view_pos) +
    (`Age` = age) +
    (`Hispanic or Latino/x` = hispanic) +
    (`Race, Black` = race_white) +
    (`Race, Black` = race_black) +
    (`Race, Native American` = race_nat) +
    (`Race, Asian or Pacific Islander` = race_asian) +
    (`Some College, or above` = college)  ~ 
    (Mean + SD) ,
  data = desc_table,
  fmt = '%.2f',
  title = 'Descriptive Statistics for Dichotomous and Numeric Variables',
  notes =c(glue("Notes: {nrow(rain)} Surveyed, Conducted {format( min(rain$date), '%B %d')} through {format(max(rain$date), '%B %d')}, 2021.")))
```


```{r desc-table-2}
#| results = "asis"


datasummary(formula = ((`Income` = income)+  
                         (`Gender` = gender)+  
                         (`Highest Education Level` = educ) + 
                         (`Plan to be Vaccinated if not` = vacc_status_future)  +
                         (`Found Info Sought Useful` = int_sought_useful)) ~ N + Percent(), 
 data = rain,
   fmt = '%.2f',
  title = 'Descriptive Statistics for Categorical Variables',
 notes =c(glue("Notes: {nrow(rain)} Surveyed, Conducted {format( min(rain$date), '%B %d')} through {format(max(rain$date), '%B %d')}, 2021.")),
 output = "kableExtra") %>%
  kable_styling(latex_options = 'HOLD_position')

# TODO reorder factors in categorical table

```


```{r clean_before_reg}
rain <- rain %>% 
  mutate(across(c(receive_i,
                  receive_i_fr_dr,
                  receive_i_fr_pers,
                  receive_i_fr_tv,
                  receive_i_fr_onlnet,
                  receive_i_fr_onlgroup,
                  int_sought,
                  int_sought_fr_pers,
                  int_sought_fr_dr,
                  int_sought_fr_onlgroup,
                  int_sought_fr_onlnet,
                  int_sought_fr_onlsearch,
                  int_sought_affect,
                  vacc_status,
                  vacc_view_pos,
                  hispanic,
                  race_white,
                  race_black,
                  race_nat,
                  race_asian, 
                  college), ~ factor(.x, levels = c(1, 0))))

regression_labels = c(
  'receive_i_fr_dr0' = 'Received Info, Doctor',
  'receive_i_fr_pers0' = 'Received Info, Person',
  'receive_i_fr_tv0' = 'Received Info, News',
  'receive_i_fr_onlnet0' = 'Received Info, Social Networking Site',
  'receive_i_fr_onlgroup0' = 'Received Info, Online Forum',
  'int_sought0' = 'Sought Info',
  'int_sought_fr_dr0' = 'Sought Info, Doctor',
  'int_sought_fr_pers0' = 'Sought Info, Person',
  'int_sought_fr_onlnet0' = 'Sought Info, Social Networking Site',
  'int_sought_fr_onlgroup0' = 'Sought Info, Online Forum',
  'int_sought_fr_onlsearch0' = 'Sought Info, Online Search',
  'age' = 'Age',
  'gender=Male' = 'Gender, Male',
  'gender=Other' = 'Gender, Other',
  'college0' = 'Some College +',
  'race_white0' = 'White',
  'race_black0' = 'Black',
  'race_nat0' = 'Native American',
  'race_asian0' = 'Asian',
  'hispanic0' = 'Hispanic or Latino/x')
```


# What predicts someone intentionally searched for information

Q171 And how about you yourself intentionally looking for information about a Covid-19 vaccine? Such information can include things such as advice, clarification, facts, and experiences.

* Yes
* No



```{r model1-table}
#| results = "asis"


mod1 <- glm(formula = int_sought ~ 
              receive_i_fr_dr +   
              receive_i_fr_pers +   
              receive_i_fr_tv +   
              receive_i_fr_onlnet +   
              receive_i_fr_onlgroup +   
              age + 
              gender + 
              race_white +   
              race_black +    
              race_nat +      
              race_asian +  
              hispanic  + 
              college,
            data = rain, family = binomial)

# library(patchwork)
# sjPlot::plot_model(m, type = "pred", terms = "receive_i_fr_dr") +
# sjPlot::plot_model(m, type = "pred", terms = "receive_i_fr_pers") +
# sjPlot::plot_model(m, type = "pred", terms = "receive_i_fr_tv") + 
# sjPlot::plot_model(m, type = "pred", terms = "receive_i_fr_onlnet") +
# sjPlot::plot_model(m, type = "pred", terms = "receive_i_fr_onlgroup")


modelsummary(mod1,
            gof_omit = 'AIC',
            # stars = TRUE,
            estimate = "{estimate}{stars}",
            title = 'What predicts someone intentionally searched for information',
            coef_map = regression_labels,
            notes = 'Exponentiated Coefficients',
            exponentiate = TRUE,
 output = "kableExtra") %>%
  kable_styling(latex_options = 'HOLD_position')

```


```{r model1-plot}
#| fig.cap='Plot of Coefficients, Model 1'

plot_summs(mod1, 
           scale = TRUE,
           coefs =  c(
             'Received Info, Doctor' = 'receive_i_fr_dr',
             'Received Info, Person' = 'receive_i_fr_pers',
             'Received Info, News' = 'receive_i_fr_tv',
             'Received Info, Social Networking Site' = 'receive_i_fr_onlnet',
             'Received Info, Online Forum' = 'receive_i_fr_onlgroup',
             'Sought Info' = 'int_sought',
             'Sought Info, Doctor' = 'int_sought_fr_dr',
             'Sought Info, Person' = 'int_sought_fr_pers',
             'Sought Info, Social Networking Site' = 'int_sought_fr_onlnet',
             'Sought Info, Online Forum' = 'int_sought_fr_onlgroup',
             'Sought Info, Online Search' = 'int_sought_fr_onlsearch',
             'Age' = 'age',
             'Gender, Male' = 'gender=Male',
             'Gender, Other' = 'gender=Other',
             'Some College +' = 'college',
             'White' = 'race_white',
             'Black' = 'race_black',
             'Native American' = 'race_nat',
             'Asian' = 'race_asian',
             'Hispanic or Latino/x' = 'hispanic'),
           robust = TRUE) +
  labs(title = 'What predicts someone intentionally searched for information', caption = 'Coefficients Scaled and robust') +
  theme_diss()
```
\newpage  

# What is associated with using different kinds of search vehicles?


Q172 How did you look for information about the Covid-19 vaccine?

*	Asking a person like friend, neighbor, or family member that I know  
*	Asking my doctor or another health professional  
*	Posted queries in an online discussion group, listserve, or other online forum like a Facebook Group or Subreddit  
*	Posted queries on a social networking site such as Facebook timeline, Twitter status update, or Linkedin  
*	Searched for my question using an online search engine such as Google or Bing   
*	Other ________________________________________________



```{r model2-table}
#| results = "asis"

part2_models <- list()

part2_models[['Person']] <- glm(formula = int_sought_fr_pers ~ 
           receive_i_fr_dr + receive_i_fr_pers + receive_i_fr_tv +    
           receive_i_fr_onlnet + receive_i_fr_onlgroup + 
           age + gender + college +
           race_white + race_black + race_nat + race_asian + hispanic,  
         data = rain, family = binomial)

part2_models[['Doctor']] <- glm(formula = int_sought_fr_dr ~ 
           receive_i_fr_dr + receive_i_fr_pers + receive_i_fr_tv +    
           receive_i_fr_onlnet + receive_i_fr_onlgroup + 
           age + gender + college +
           race_white + race_black + race_nat + race_asian + hispanic,  
         data = rain, family = binomial)

part2_models[['Online Forum']] <- glm(formula = int_sought_fr_onlgroup ~ 
           receive_i_fr_dr + receive_i_fr_pers + receive_i_fr_tv +    
           receive_i_fr_onlnet + receive_i_fr_onlgroup + 
           age + gender + college +
           race_white + race_black + race_nat + race_asian + hispanic,  
         data = rain, family = binomial)

part2_models[['Social Networking\nSite']] <- glm(formula = int_sought_fr_onlnet ~ 
           receive_i_fr_dr + receive_i_fr_pers + receive_i_fr_tv +    
           receive_i_fr_onlnet + receive_i_fr_onlgroup + 
           age + gender + college +
           race_white + race_black + race_nat + race_asian + hispanic,  
         data = rain, family = binomial)

part2_models[['Online Search']] <- glm(formula = int_sought_fr_onlsearch ~ 
           receive_i_fr_dr + receive_i_fr_pers + receive_i_fr_tv +    
           receive_i_fr_onlnet + receive_i_fr_onlgroup + 
           age + gender + college +
           race_white + race_black + race_nat + race_asian + hispanic,  
         data = rain, family = binomial)

modelsummary(part2_models,
             estimate = "{estimate}{stars}",
            gof_omit = 'AIC',
            coef_map = regression_labels,
            notes = 'Note: Exponentiated Coefficients',
            title = 'What predicts someone intentionally searched for information, by vehicle of information search',
            exponentiate = TRUE,
 output = "kableExtra") %>%
  kable_styling(latex_options = 'HOLD_position')

# TODO ADD IN N To TABLE


```


\newpage

# Researching how you search for vaccination information affects vaccination status
```{r model3-table}
#| results = "asis"


mod3 <- glm(formula = vacc_view_pos ~ receive_i_fr_dr +   
           receive_i_fr_pers +      
           receive_i_fr_tv +    
           receive_i_fr_onlnet +    
           receive_i_fr_onlgroup + 
           int_sought_fr_pers +  
           int_sought_fr_dr +    
           int_sought_fr_onlgroup +
           int_sought_fr_onlnet +
           int_sought_fr_onlsearch +
           age + 
           gender + 
           race_white +   
           race_black +    
           race_nat +      
           race_asian + hispanic +     
           college,  
         data = rain, family = binomial)


modelsummary(mod3,
            gof_omit = 'AIC',
            estimate = "{estimate}{stars}",
            title = 'Does receiving or searching for information predict vaccination status?',
            notes = 'Note: Exponentiated Coefficients',
            coef_map = regression_labels,
            exponentiate = TRUE,
 output = "kableExtra") %>%
  kable_styling(latex_options = 'HOLD_position')
```



```{r model3-plot}
#| fig.cap='Plot of Coefficients, Model 3'

plot_summs(mod3,
           scale = TRUE,
           coefs =  c(
             'Received Info, Doctor' = 'receive_i_fr_dr',
             'Received Info, Person' = 'receive_i_fr_pers',
             'Received Info, News' = 'receive_i_fr_tv',
             'Received Info, Social Networking Site' = 'receive_i_fr_onlnet',
             'Received Info, Online Forum' = 'receive_i_fr_onlgroup',
             'Sought Info' = 'int_sought',
             'Sought Info, Doctor' = 'int_sought_fr_dr',
             'Sought Info, Person' = 'int_sought_fr_pers',
             'Sought Info, Social Networking Site' = 'int_sought_fr_onlnet',
             'Sought Info, Online Forum' = 'int_sought_fr_onlgroup',
             'Sought Info, Online Search' = 'int_sought_fr_onlsearch',
             'Age' = 'age',
             'Gender, Male' = 'gender=Male',
             'Gender, Other' = 'gender=Other',
             'Some College +' = 'college',
             'White' = 'race_white',
             'Black' = 'race_black',
             'Native American' = 'race_nat',
             'Asian' = 'race_asian',
             'Hispanic or Latino/x' = 'hispanic'),
           robust = TRUE) +
  labs(title = 'Does receiving or searching for information predict vaccination status?', 
       caption = 'Coefficients Scaled and robust') +
  theme_diss()

# library(patchwork)
# sjPlot::plot_model(m, type = "pred", terms = "receive_i_fr_dr") +
# sjPlot::plot_model(m, type = "pred", terms = "receive_i_fr_onlnet") +
# sjPlot::plot_model(m, type = "pred", terms = "receive_i_fr_onlgroup") + 
# sjPlot::plot_model(m, type = "pred", terms = "int_sought_fr_dr") +
# sjPlot::plot_model(m, type = "pred", terms = "college") 
```

# Bibliography

# Appendix 1: Survey Questions

*Q181*: Now, we're going to transition a bit to ask you about the information you received during the Covid-19 pandemic.

*Q170*: In the past 12 months, without searching for it, did you receive information about the Covid-19 vaccine from … (check all sources you received information from)  

*	your doctor or other health professional?   (1) 
*	a person like friend, neighbor, or family member that you know ?  (9) 
*	From television news channel or the newspaper?  (10) 
*	From an online discussion group, listserve, or other online forum including a Facebook group or subreddit?  (11) 
*	From a social networking site such as Facebook timeline, Twitter status update, or linkedin?  (12) 
*	Other  (13) ________________________________________________

*Q171*: And how about you yourself intentionally looking for information about a Covid-19 vaccine? Such information can include things such as advice, clarification, facts, and experiences. 

*	Yes  (4) 
*	No  (5) 

*Q172*: How did you look for information about the Covid-19 vaccine?  

*	Asking a person like friend, neighbor, or family member that I know  (1) 
*	Asking my doctor or another health professional  (4) 
*	Posted queries in an online discussion group, listserve, or other online forum like a Facebook Group or Subreddit  (5) 
*	Posted queries on a social networking site such as Facebook timeline, Twitter status update, or Linkedin  (6) 
*	Searched for my question using an online search engine such as Google or Bing  (7) 
*	Other  (8) ________________________________________________

*Q173*: What sort of information did you search for? 
 Separate different topics with a comma or semi-colon. 
___________


*Q174*: How useful was the information you found?  

*	Extremely useful  (22) 
*	Very useful  (23) 
*	Moderately useful  (24) 
*	Slightly useful  (25) 
*	Not at all useful  (26) 

*Q175*: Did the information you learned affect your decision to get vaccinated against Covid-19?  

*	Yes  (39) 
*	No  (40) 

*Q179*: Did you receive a Covid-19 vaccine?  

*	Yes  (9) 
*	No  (10) 
*	I'm unsure or would not like to respond  (11) 

*Q180*: Do you plan to receive a vaccine for the prevention of the Covid-19 virus?  

*	Definitely not  (9) 
*	Probably not  (10) 
*	Might or might not  (11) 
*	Probably yes  (12) 
*	Definitely yes  (13) 
*	I would not like to respond  (14) 


*gender*: What is your gender?  

*	Male  (1) 
*	Female  (2) 
*	Other  (3) ________________________________________________
*	Prefer not to say  (4) 

*hispanic*: Are you Hispanic, Latino/a/x, or Latin American Origin?  

*	Yes  (1) 
*	No  (2) 

*race*: What is your race? If you are "mixed race", select all that apply.  

*	White  (1) 
*	Black or African American  (2) 
*	American Indian or Alaskan Native  (3) 
*	Asian (please specify):  (4) ________________________________________________
*	Other (please specify):  (5) ________________________________________________
*	Prefer not to say  (6) 

*educ*: What is the highest level of education that you have completed?   

*	Less than high school  (1) 
*	High school graduate  (2) 
*	Some college  (3) 
*	Associate's or Technical degree  (4) 
*	Bachelor's degree  (5) 
*	Graduate or professional degree  (6) 

*income*: We would be interested to know roughly what your total household income
before taxes is. We mean income from all sources, including welfare, stock
dividends, other household members' income, etc. In 2020, in which bracket did your total family income fall?  

*	Under $1,000  (1) 
*	\$1,000 to \$9,999   (2) 
*	\$10,000 to \$19,999  (3) 
*	\$20,000 to \$29,999  (4) 
*	\$30,000 to \$39,999  (5) 
*	\$40,000 to \$49,999  (6) 
*	\$50,000 to \$59,999  (7) 
*	\$60,000 to \$74,999  (8) 
*	\$75,000 to \$89,999   (9) 
*	\$90,000 to \$109,999  (10) 
*	\$110,000 to \$129,999  (11) 
*	\$130,000 to \$149,999  (12) 
*	\$150,000 or over  (13) 
*	Don't know  (14) 

*age*: What is your age? (in years)  

________________________________________________________________

